Pruning Subsequence Search with Attention-Based Embedding

### 2015-09-18 paper.tex
Add abstract

\title{Pruning Sequence Search with Attention-Based Embedding}

@@

\begin{abstract}
\end{abstract}

\begin{keywords}
\end{keywords}

@@

\cite{rakthanmanon2012searching}

>>>>

\title{Pruning Subsequence Search with Attention-Based Embedding}

@@

\begin{abstract}
Finding the most similar sequence to a query in a database of sequences can be prohibitively expensive when the database size is large.
Typically, the scalability of different approaches are dependent on various ``pruning'' techniques, which use heuristics to avoid expensive comparisons against a large subset of the database.
We present an approximate pruning technique which involves embedding sequences in a Euclidean space.
Sequences are embedded using a convolutional network with a form of attention which integrates over time, which is trained using matching and non-matching pairs of sequences.
By using fixed-length embeddings, our pruning method effectively runs in constant time, making it many orders of magnitude faster when compared to full Dynamic Time Warping-based matching.
We demonstrate the effectiveness of our approach on a large-scale musical score-to-audio recording retrieval task.
\end{abstract}

\begin{keywords}
Sequence Retrieval, Attention-Based Models, Convolutional Networks, Dynamic Time Warping, Pruning
\end{keywords}

@@

\cite{rakthanmanon2012searching} \cite{papapetrou2011embedding}
